Visualization

### 2023-02-09 Code/NewPlots.Rmd
Manuscript Update

```{r}
graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

  df <- data.frame(n, CI, t, cov, LB, UB)
  library(ggplot2)
  ggplot(df, aes(x = n, y = cov)) +
    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
    geom_line() +
    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
    facet_grid(t ~ CI)
}
```

```{r}
theta <- 0.1
target <- c(0, 1, theta)
cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))

graph_bts(cov, theta, target, width = 50)
ggsave('../Manuscript/figures/plot_.1.pdf')
```
```{r}
theta <- 0.3
target <- c(0, 1, theta)
cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))

graph_bts(cov, theta, target, width = 25)
ggsave('../Manuscript/figures/plot_.3.pdf')
```
```{r}
theta <- 0.5
target <- c(0, 1, theta)
cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))

graph_bts(cov, theta, target, width = 10)
ggsave('../Manuscript/figures/plot_.5.pdf')
```

>>>>

```{r}
graph_bts <- function(cov, phi, target, width, trans = 'identity', nrep = 1000, sizes = c(100, 200, 300, 400, 500, 600, 700), types = c('estCI', 'bcaCIest'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

  df <- data.frame(n, CI, t, cov, LB, UB)
  library(ggplot2)
  ggplot(df, aes(x = n, y = cov)) +
    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
    geom_line() +
    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
    facet_grid(factor(t, levels = parameters) ~ factor(CI, levels = types)) +
    scale_y_continuous(trans=trans)
}
```

```{r}
phi <- -.4
target <- c(0, 1, phi)
cov <- c(mychk(sim_n.4_1h, target), mychk(sim_n.4_2h, target), mychk(sim_n.4_3h, target), mychk(sim_n.4_4h, target), mychk(sim_n.4_5h, target), mychk(sim_n.4_6h, target), mychk(sim_n.4_7h, target))

graph_bts(cov, phi, target, width = 10)
ggsave('../Manuscript/figures/plot_n.4.pdf')
```
```{r}
phi <- -.2
target <- c(0, 1, phi)
cov <- c(mychk(sim_n.2_1h, target), mychk(sim_n.2_2h, target), mychk(sim_n.2_3h, target), mychk(sim_n.2_4h, target), mychk(sim_n.2_5h, target), mychk(sim_n.2_6h, target), mychk(sim_n.2_7h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_n.2.pdf')
```

```{r}
phi <- 0
target <- c(0, 1, phi)
cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target), mychk(sim_0_6h, target), mychk(sim_0_7h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_0.pdf')
```
```{r}
phi <- .2
target <- c(0, 1, phi)
cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target), mychk(sim_.2_6h, target), mychk(sim_.2_7h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_.2.pdf')
```
```{r}
phi <- .4
target <- c(0, 1, phi)
cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target), mychk(sim_.4_6h, target), mychk(sim_.4_7h, target))

graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_.4.pdf')
```

### 2023-02-09 Code/simulation.Rmd
Manuscript Update

    ## Percentile interval
    mbts <- apply(bts$t, 2, mean)
    crit <- 
      apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
    ## alpha/2 and 1 - alpha/2 critical values 
    ## of pseudo-estimate - mean of pseudo-estimates
    crit2 <- 
      apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
    ## alpha/2 and 1 - alpha/2 critical values 
    ## of pseudo-estimate - original estimate

    ## interval centered around...
    estCI <- sweep(crit, 2, bts$t0, FUN = '+') # original estimate
    ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
    mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
    ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
    altCI <- sweep(-crit[order(2:1),], 2, bts$t0, FUN = '+') # both
    ## LB: bts$t0 - (1 - alpha/2) crit, UB: bts$t0 - alpha/2 crit and
    ## LB: mbts - (1 - alpha/2) crit2, UB: mbts - alpha/2 crit2

    ## BCa interval
    z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
    thetajack <- sapply(1: (n / blksize), 
                        function(i) 
                          statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
    a <- apply(thetajack, 1, e1071::skewness) / 6
    alpha1 <- pnorm(
      z0 + (z0 + qnorm(alpha/2)) / (1 - a * (z0 + qnorm(alpha/2))))
    alpha2 <- pnorm(
      z0 + (z0 + qnorm(1 - alpha/2)) / (1 - a * (z0 + qnorm(1 - alpha/2))))
    crit3 <- sapply(1:length(bts$t0), function(i) 
      quantile(t(t(bts$t[,i]) - mbts[i]), prob = c(alpha1[i], alpha2[i]))) 
    ## alpha1 and alpha2 critical values 
    ## of pseudo-estimate - mean of pseudo-estimates
    crit4 <- sapply(1:length(bts$t0), function(i) 
      quantile(t(t(bts$t[,i]) - bts$t0[i]), prob = c(alpha1[i], alpha2[i])))
    ## alpha1 and alpha2 critical values 
    ## of pseudo-estimate - original estimate

    ## interval centered around...
    bcaCIest <- sweep(crit3, 2, bts$t0, FUN = '+') # original estimate
    ## LB: bts$t0 + alpha1 crit3, UB: bts$t0 + alpha2 crit3
    bcaCImbt <- sweep(crit4, 2, mbts, FUN = '+') # mean of pseudo-estimates
    ## LB: mbts + alpha1 crit4, UB: mbts + alpha2 crit4
    bcaCIalt <- sweep(-crit3[order(2:1),], 2, bts$t0, FUN = '+') # both
    ## LB: bts$t0 - alpha2 crit3, UB: bts$t0 - alpha1 crit3 and
    ## LB: mbts - alpha2 crit4, UB: mbts - alpha1 crit4

    ## return all intervals
    c(estCI, mbtCI, altCI, bcaCIest, bcaCImbt, bcaCIalt)
}

@@

@@

@@

@@

@@

>>>>

    ## Percentile interval
    mbts <- apply(bts$t, 2, mean)
    crit <- 
      apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
    ## alpha/2 and 1 - alpha/2 critical values 
    ## of pseudo-estimate - mean of pseudo-estimates
    # crit2 <- 
    #  apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
    ## alpha/2 and 1 - alpha/2 critical values 
    ## of pseudo-estimate - original estimate

    ## interval centered around...
    estCI <- sweep(crit, 2, bts$t0, FUN = '+') # original estimate
    ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
    # mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
    ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
    # altCI <- sweep(-crit[order(2:1),], 2, bts$t0, FUN = '+') # both
    ## LB: bts$t0 - (1 - alpha/2) crit, UB: bts$t0 - alpha/2 crit and
    ## LB: mbts - (1 - alpha/2) crit2, UB: mbts - alpha/2 crit2

    ## BCa interval
    z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
    thetajack <- sapply(1: (n / blksize), 
                        function(i) 
                          statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
    a <- apply(thetajack, 1, e1071::skewness) / 6
    alpha1 <- pnorm(
      z0 + (z0 + qnorm(alpha/2)) / (1 - a * (z0 + qnorm(alpha/2))))
    alpha2 <- pnorm(
      z0 + (z0 + qnorm(1 - alpha/2)) / (1 - a * (z0 + qnorm(1 - alpha/2))))
    crit3 <- sapply(1:length(bts$t0), function(i) 
      quantile(t(t(bts$t[,i]) - mbts[i]), prob = c(alpha1[i], alpha2[i]))) 
    ## alpha1 and alpha2 critical values 
    ## of pseudo-estimate - mean of pseudo-estimates
    # crit4 <- sapply(1:length(bts$t0), function(i) 
    #  quantile(t(t(bts$t[,i]) - bts$t0[i]), prob = c(alpha1[i], alpha2[i])))
    ## alpha1 and alpha2 critical values 
    ## of pseudo-estimate - original estimate

    ## interval centered around...
    bcaCIest <- sweep(crit3, 2, bts$t0, FUN = '+') # original estimate
    ## LB: bts$t0 + alpha1 crit3, UB: bts$t0 + alpha2 crit3
    # bcaCImbt <- sweep(crit4, 2, mbts, FUN = '+') # mean of pseudo-estimates
    ## LB: mbts + alpha1 crit4, UB: mbts + alpha2 crit4
    # bcaCIalt <- sweep(-crit3[order(2:1),], 2, bts$t0, FUN = '+') # both
    ## LB: bts$t0 - alpha2 crit3, UB: bts$t0 - alpha1 crit3 and
    ## LB: mbts - alpha2 crit4, UB: mbts - alpha1 crit4

    ## return all intervals
    c(estCI, bcaCIest)
}

@@

```{r ar = -.4, n = 700}
n <- 700
blksize <- 9
phi <- -.4
target <- c(0, 1, phi)
set.seed(6789)
sim_n.4_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_7h,"../Data/Raw/sim_n.4_7h.csv", row.names = FALSE)
mychk(sim_n.4_7h, target)
```

@@

```{r ar = -.2, n = 700}
n <- 700
blksize <- 9
phi <- -.2
target <- c(0, 1, phi)
set.seed(6789)
sim_n.2_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_7h,"../Data/Raw/sim_n.2_7h.csv", row.names = FALSE)
mychk(sim_n.2_7h, target)
```

@@

```{r ar = 0, n = 700}
n <- 700
blksize <- 9
phi <- 0
target <- c(0, 1, phi)
set.seed(6789)
sim_0_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_7h,"../Data/Raw/sim_0_7h.csv", row.names = FALSE)
mychk(sim_0_7h, target)
```

@@

```{r ar = .2, n = 700}
n <- 700
blksize <- 9
phi <- .2
target <- c(0, 1, phi)
set.seed(6789)
sim_.2_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_7h,"../Data/Raw/sim_.2_7h.csv", row.names = FALSE)
mychk(sim_.2_7h, target)
```

@@

```{r ar = .4, n = 700}
n <- 700
blksize <- 9
phi <- .4
target <- c(0, 1, phi)
set.seed(6789)
sim_.4_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_7h,"../Data/Raw/sim_.4_7h.csv", row.names = FALSE)
mychk(sim_.4_7h, target)
```
